Assessing Power of the California Microhap Baseline for GSI (and calculating Fst)

### 2025-03-14 002-GSI_and_Fst.Rmd
Get some counts

>>>>

## Get a quick summary of number of collections and samples by ecotype

One of the reviewers wanted summaries in the text.  That's a great idea.
Here we get the numbers that we need.  
```{r}
# total fish:
sum(fbmet4$N)
```

```{r}
# numbers of samples and collection by ecotype
fbmet4 %>%
  group_by(`Run Timing`) %>%
  summarise(
    num_collections = n(),
    num_samples = sum(N)
  )
```
